### 2018-05-16 Paper/examples.tex
..
.

>>>>

In this test problem, we consider an undamped non-linear oscillator with only one degree of
freedom as illustrated below in Figure~\ref{fig:osc}.

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.6\textwidth]{./Figures/oscillator}
\caption{Schematic illustration of an undamped non-linear oscillator system with one degree of freedom.}
\label{fig:osc}
\end{center}
\end{figure}

The above system has been studied extensively for its reliability using the following state function~\cite{Bucher:1989, 
Bucher:1990,Rajashekhar:1993,Schueremans:2005,Gayton:2003}:

\be
g(\bm{X}) = 3r - \left|z_\text{max}\right| = 3r - \left|\frac{2F}{m\omega_0^2}\sin\left(\frac{\omega_0t_1}{2}\right)\right|
\ee
